### 2014-07-27 Pero_Transcriptome.tex
1132

The raw sequence reads were error corrected using the software bless \cite{Heo:2014cb}, using kmer=25, based on the developers recommendations. The error corrected adapter and quality trimmed following recommendations from MacManes \cite{MacManes:2014io} and Mbandi \cite{Christoffels:2014bg}. Specifically, adapter sequence contamination was removed, and low quality nucleotides (defined as \textsc{Phred} \textless 2) were removed using the program Trimmomatic version 0.32  \cite{Lohse:2012fg}. We concatenated sequence data from each reference tissue type and assembled them jointly using Trinity version released 17 July 2014 \cite{Haas:2013jq}. We used flags indicating the stranded nature of sequencing reads and set maximum allowable physical distance between read pairs to 999nt. The assembly was conducted on a lunix workstation with 64 cores and 512Gb RAM. To filter the raw sequence assembly, I estimated TPM for each assembled sequence using bwa-mem version 0.75 \cite{Li:2013wn} and eXpress version 1.51 \cite{Roberts:2012dh}, removing all contigs whose expression was less than TPM=1 \cite{Haas:2013jq}. \\

@@

@@

%\section*{References}
% The bibtex filename
\bibliography{formatted1.bib}

>>>>

The raw sequence reads were error corrected using the software bless \cite{Heo:2014cb}, using kmer=25, based on the developers recommendations. The error corrected adapter and quality trimmed following recommendations from MacManes \cite{MacManes:2014io} and Mbandi \cite{Christoffels:2014bg}. Specifically, adapter sequence contamination was removed, and low quality nucleotides (defined as \textsc{Phred} \textless 2) were removed using the program Trimmomatic version 0.32  \cite{Lohse:2012fg}. We concatenated sequence data from each reference tissue type and assembled them jointly using Trinity version released 17 July 2014 \cite{Haas:2013jq}. We used flags indicating the stranded nature of sequencing reads and set maximum allowable physical distance between read pairs to 999nt. The assembly was conducted on a lunix workstation with 64 cores and 512Gb RAM. To filter the raw sequence assembly, I estimated TPM for each assembled sequence using bwa-mem version 0.75 \cite{Li:2013wn} and eXpress version 1.51 \cite{Roberts:2012dh}, removing all contigs whose expression was less than TPM=1 \cite{Haas:2013jq}. The resulting assembly was characterized using the software package transrate (\url{https://github.com/Blahah/transrate})

\\

@@

\subsection*{Natural Selection}

To characterize natural selection on several genes related to water and ion homeostasis, we identified several of the transcripts identified as experiencing positive selection in a resent work on desert-adapter \textit{Dipodomys} rodents. The coding sequence corresponding to these genes, Solute Carrier family 2 member 9  (Slc2a9) and the Vitamin D3 receptor (Vdr), were extracted from the dataset, aligned using the software MACSE \cite{Ranwez:2011kj} to homologous sequences identified by the conditional reciprocal best blast procedure (CRBB, \cite{Aubry:2014en}) implemented in transrate. These alignments were inputted into the software codeABC version 1.6.0 \cite{Lopes:2013fd}.

@@

%\section*{References}
% The bibtex filename
\bibliography{formatted.bib}
